# Regressionsmodelle: Erweiterungen

```{r setup, include=FALSE}
if(Sys.getenv("USERNAME") == "filse" ) .libPaths("D:/R-library4") 
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, dpi=300)
pacman::p_load(mfx, tidyverse, hrbrthemes, estimatr, ivreg, fixest, sandwich, marginaleffects,
               lmtest, margins, vtable, broom, modelsummary, kableExtra)

mark_color <- "grey25"
color1x =  "#00519E" # uol farbe
colorhex <- "#FCFCFC" #"#FCF9F0FF"7
colorhex <- NA #"#FCF9F0FF"7
library(extrafont)
windowsFonts(Nunito=windowsFont("Nunito Sans"))

theme_x <- 
  theme_minimal(base_family = "Nunito",base_size = 10) +
  theme(
    plot.background = element_rect(fill = colorhex, linetype = 1, colour = NA),
    rect = element_rect(fill = colorhex, linetype = 1, colour = NA),
    axis.text =  element_text(color = mark_color,face = "plain", size = rel(.75), angle = 0), 
    axis.title = element_text(color = mark_color,face = "plain", size = rel(1), angle = 0), 
    axis.title.y = element_text(color = mark_color,face = "plain", angle = 0,vjust = .5), 
    axis.ticks = element_blank(),
    axis.line = element_line(size = .1), 
    panel.grid = element_line(colour = "grey81", linetype = 1, size = .15), 
    panel.grid.minor.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    plot.subtitle = element_text(hjust=0),
    plot.caption = element_text(hjust=1, size = rel(1.2), color = mark_color),
    plot.margin = unit(c(1, 1, 1, 1), "lines"))

theme_set(theme_x)
```
```{r}
library(tidyverse)
```

Nach den basics für Regressionsmodelle sehen wir uns in diesem Kapitel einige hilfreiche Erweiterungen von Regressionsmodellen in R an

Die folgenden Beispiele basieren vornehmlich auf dem `starwars`-Datensatz aus `{dplyr}`, hier ein kurzer Blick in die Daten:

```{r starwars}
starwars
```

Unser Beispiel ist ein simples: der Zusammenhang zwischen Größe und Gewicht der Star Wars Helden:
```{r mod1}
mod1 <- lm(mass ~ height, data = starwars)
```

## "tidy" Regressionskoeffizienten mit `{broom}`

While it's easy to extract regression coefficients via the `summary()` function, in practice I always use the **broom** package ([link ](https://broom.tidyverse.org/)) to do so. **broom** has a bunch of neat features to convert regression (and other statistical) objects into "tidy" data frames. This is especially useful because regression output is so often used as an input to something else, e.g. a plot of coefficients or marginal effects. Here, I'll use `broom::tidy(..., conf.int = TRUE)` to coerce the `mod1` regression object into a tidy data frame of coefficient values and key statistics.

```{r mod1_tidy}
# library(broom) ## schon geladen als Teil des tidyverse
tidy(mod1, conf.int = TRUE)
```

Again, I could now pipe this tidied coefficients data frame to a **ggplot2** call, using saying `geom_pointrange()` to plot the error bars. Feel free to practice doing this yourself now, but we'll get to some explicit examples further below.

**broom** has a couple of other useful functions too. For example, `broom::glance()` summarises the model "meta" data (R<sup>2</sup>, AIC, etc.) in a data frame.

```{r mod1_glance}
glance(mod1)
```

By the way, if you're wondering how to export regression results to other formats (e.g. LaTeX tables), don't worry: We'll [get to that](#regression-tables) at the end of the lecture.


## Nonstandard errors

> Dealing with statistical irregularities (heteroskedasticity, clustering, etc.) is a fact of life for empirical researchers. [Grant McDermott](https://raw.githack.com/uo-ec607/lectures/master/08-regression/08-regression.html#Nonstandard_errors)

Die gute Nachricht ist, dass R eine ganze Reihe an Möglichkeiten bietet, Standard-Fehler zu korrigieren.
Unter anderem mit [{sandwich}](http://sandwich.r-forge.r-project.org/articles/sandwich.html) oder [{estimatr}](https://declaredesign.org/r/estimatr/articles/getting-started.html)).
Einse sehr einfache Variante ist die Korrektur von Standardfehlern in `{modelsummary}`, die wir uns etwas genauer ansehen:


Wir können sog. *heteroskedasticity-consistent* (HC) "robuste" Standardfehler mit der `vcov`-Option `HC` in `modelsummary()` anfordern. 
Die Hilfe-Seite für `{modelsummary}` bietet eine [Liste mit allen Optionen](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#vcov).

Eine Option ist auch `stata`, um Ergebnisse aus Statas `, robust` zu replizieren. 
[Hier mehr](https://declaredesign.org/r/estimatr/articles/stata-wls-hat.html) zu den Hintergründen und Unterschieden.

```{r mod1_robust_stata}
modelsummary::modelsummary(list(mod1,mod1,mod1,mod1),vcov = c("classical","HC","HC2","stata"))
```

## Fixed effects Modelle mit `{fixest}`

```{r}
#| eval: false
install.packages("fixest")
```

[`{fixest}`](https://lrberge.github.io/fixest)) ist zwar noch relativ neu, aber bietet eine große Auswahl an Möglichkeiten: [logitische Modelle](#10_log_reg.qmd##feglm), mehr-dimensionale Fixed Effects, Multiway clustering, ...
Und es ist sehr schnell, [bspw. schneller](https://lrberge.github.io/fixest/#benchmarking) als Statas `reghdfe`. 
Für mehr Details empfiehlt sich die [Vignette](https://lrberge.github.io/fixest/articles/fixest_walkthrough.html).

Die zentrale Funktion zur Schätzung linearer FE-Regressionsmodelle ist `feols()` - sie funktioniert ganz ähnlich zu `lm()`. 
Auch hier geben wir wieder eine Formel nach dem Schema `abhängige Variabe ~ unabhängige Variable(n)` an. 
Wir fügen lediglich mit `|` die Variable hinzu, welche die FEs festlegt:

```{r ols_fe, message=FALSE}
library(fixest)
ols_fe<- feols(mass ~ height | species, data = starwars) ## Fixed effect(s) go after the "|"
ols_fe
```

`{fixest}` clustert automatisch die Standardfehler entlang der FE-Variable (hier also `species`).


ut to preview things, you can specify the standard errors you want at estimation time... or you can adjust the standard errors for any existing model via `summary.fixest()`. 
For example, here are two equivalent ways to specify vanilla (iid) standard errors:

```{r ols_fe_standard_et, message=FALSE}
feols(mass ~ height | species,data = starwars, se = 'standard')
feols(mass ~ height | species,data = starwars, cluster = ~ species + homeworld)
```


Before continuing, let's quickly save a "tidied" data frame of the coefficients for later use. I'll use iid standard errors again, if only to show you that the `broom::tidy()` method for `fixest` objects also accepts an `se` argument. This basically just provides another convenient way for you to adjust standard errors for your models on the fly.

```{r coefs_fe}
# coefs_fe = tidy(summary(ols_fe, se = 'standard'), conf.int = TRUE) ## same as below
coefs_fe = tidy(ols_fe, se = 'standard', conf.int = TRUE)
```


### geclusterte Standardfehler

Clustered standard errors is an issue that most commonly affects panel data. 
But here's a quick example of clustering with `estimatr::lm_robust()` just to illustrate:

```{r mod1_robust_clustered, warning = FALSE}
estimatr::lm_robust(mass ~ height, data = starwars, clusters = homeworld)
modx <- lm(mass ~ height, data = starwars)
# modelsummary(list(modx), vcov = ~homeworld)
```




## Standardfehler 

We've now seen the various options that **fixest** has for specifying different standard error structures. 
In short, you invoke either of the `se` or `cluster` arguments. 
Moreover, you can choose to do so either at estimation time, or by adjusting the standard errors for an existing model post-estimation (e.g. with `summary.fixest(mod, cluster = ...)`). There are two additional points that I want to draw your attention to.

First, if you're coming from another statistical language, adjusting the standard errors post-estimation (rather than always at estimation time) may seem slightly odd. But this behaviour is actually extremely powerful, because it allows us to analyse the effect of different error structures *on-the-fly* without having to rerun the entire model again. **fixest** is already the fastest game in town, but just think about the implied time savings for really large models.^[To be clear, adjusting the standard errors via, say, `summary.fixest()` completes instantaneously.] I'm a huge fan of the flexibility, safety, and speed that on-the-fly standard error adjustment offers us. 

Ein [Blog Post von Grant Mcdermott](https://grantmcdermott.com/better-way-adjust-SEs/) argumentiert noch etwas ausführlicher.

Second, reconciling standard errors across different software is a much more complicated process than you may realise. There are a number of unresolved theoretical issues to consider --- especially when it comes to multiway clustering --- and package maintainers have to make a number of arbitrary decisions about the best way to account for these. 

Siehe auch die Diskussion [hier](https://github.com/sgaure/lfe/issues/1#issuecomment-530643808) 

`{fixest}`) has taken the time to write out a [detailed vignette](https://lrberge.github.io/fixest/articles/standard_errors.html) about how to replicate standard errors from other methods and software packages.
[Detailliertes Paper](http://sandwich.r-forge.r-project.org/articles/jss_2020.html) von den Autoren von `{sandwich}` zu diesem Thema. 

